---
title: "MC"
author: "Andrey Bydanov"
date: "2023-01-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
#install.packages("Hmisc")
library(Hmisc)

```

## 
Well, we have our data here. Let's have a look on it.  
```{r}
# data preparing 
soccer_general <- read.csv("soccer.csv", sep=";")[, 2:6] %>%
  mutate(Position = as.factor(Position),
         Nationality = as.factor(Nationality),
         Age = as.numeric(Age),
         Height = as.numeric(Height)) %>%
  filter(Nationality %in% c("Spanish", "Italian", "German", "English", "Argentinian"))

set.seed(1)

soccer_wrk <- soccer_general[sample(1:nrow(soccer_general), 150), ] %>%
  mutate(Nationality = factor(Nationality))
soccer_wrk
```

Build a plot:

```{r}
# using boxplot for heigh distribution visualizing within footbal groups 
pd <- position_dodge(0.1)

ggplot(data = soccer_general, 
       aes(x = soccer_general$Position, y = soccer_general$Height)) +
  geom_boxplot() + 
  stat_summary(fun.data="mean_cl_normal", geom="line", colour="blue")+
  stat_summary(fun.data="mean_cl_normal", conf.int=0.95, geom="errorbar", 
               width=0.1, linetype=2, colour="blue")+
  stat_summary(fun.data="mean_cl_normal", geom="point", size=3, 
               shape=1, colour="blue")+
  labs(title="Heigh and Position")

summary(soccer_general$Position)
```

```{r}
# forming samples with position groups
forward <- soccer_general %>% filter(Position == "Forward") %>% pull(Age) %>% na.omit()
defender <- soccer_general %>% filter(Position == "Defender") %>% pull(Age) %>% na.omit()
goalkeeper <- soccer_general %>% filter(Position == "Goalkeeper") %>%pull(Age) %>% na.omit()
middle <- soccer_general %>% filter(Position == "Midfielder") %>% pull(Age) %>% na.omit()

```

```{r}
# create CI for groups comparing 

t.test(defender, forward)$conf.int
mean(defender) - mean(forward)

t.test(defender, goalkeeper)$conf.int
mean(defender) - mean(goalkeeper)

t.test(defender, middle)$conf.int
mean(defender) - mean(middle)

t.test(goalkeeper, forward)$conf.int
mean(goalkeeper) - mean(forward)

t.test(forward, middle)$conf.int
mean(forward) - mean(middle)

t.test(middle, goalkeeper)$conf.int
mean(middle) - mean(goalkeeper)

# I know, here I must apply a useful function to simplfy this work, but I didn't...
```
Here we can see that forward and middle players have no statistically significant difference in their means estimates. 

Let's perform p-value estimation of mean difference - 
```{r}
# pairwise t-test performing without p.adjust.method
x <- data.frame(data=c(forward,defender,goalkeeper,middle),
                key=c(
                  rep("forward", length(forward)),
                  rep("defender", length(defender)),
                  rep("goalkeeper", length(goalkeeper)),
                  rep("middle", length(middle))) )

pairwise.t.test(x$data, x$key, pool.sd=FALSE)
```


```{r}
# pairwise t-test performing with Holm p.adjust.method
x <- data.frame(data=c(forward,defender,goalkeeper,middle),
                key=c(
                  rep("forward", length(forward)),
                  rep("defender", length(defender)),
                  rep("goalkeeper", length(goalkeeper)),
                  rep("middle", length(middle))) )

pairwise.t.test(x$data, x$key, pool.sd=FALSE, 
                p.adjust.method = "holm")
```
```{r}
# pairwise t-test performing with B.Hochberg p.adjust.method
x <- data.frame(data=c(forward,defender,goalkeeper,middle),
                key=c(
                  rep("forward", length(forward)),
                  rep("defender", length(defender)),
                  rep("goalkeeper", length(goalkeeper)),
                  rep("middle", length(middle))) )

pairwise.t.test(x$data, x$key, pool.sd=FALSE, 
                p.adjust.method = "hochberg")
```
It is looks like almost all groups except forward-midles have differing estimates of means - results we have got earlier with CIs. And I suppose there is no false estimates!

```{r}

```

