---
title: "MC_HW2"
author: "Andrey Bydanov"
date: "2023-01-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(multcomp)
library(dplyr)

```

## 1

Let's prepare our data like we have done earlier. 
```{r}
soccer_general <- read.csv("soccer.csv", sep=";")[, 2:6] %>% 
    mutate(Position = as.factor(Position), 
    Nationality = as.factor(Nationality), 
    Age = as.numeric(Age), 
    Height = as.numeric(Height)
) %>% 
filter(Nationality %in% c("Spanish", "Italian", "German", "English", "Argentinian")) 
set.seed(1) 
soccer_wrk <- soccer_general[sample(1:nrow(soccer_general), 150), ] %>% 
    mutate(Nationality = factor(Nationality))
```



```{r}
oneway.test(Height ~ Position, data = soccer_wrk)
```
As we see, p-value < 0.05 - it means we can reject H0 implying there is no any dependencies between heigh and player position. 

## 2 
Perform HBW test 
```{r}
m0 <- lm(Height ~ Position, data = soccer_wrk)
HBW.comp <- m0 %>%  glht(linfct = mcp(Position = "Tukey"))
HBW.comp %>% summary()
HBW.comp %>% confint()
HBW.comp %>% plot(xlab  = "Height difference (cm)")
```
Here we see that true difference have several groups - F and D, M and F - the first pair have not been recognised in previous tests with CIs.But according to p-values, M-F and F-D pairs have no significant difference in their estimates and we have no difference in heigh between this groups. 

## 3 
Previously we reported that M-F group have no significant difference in their group means but here we show that this statement also have no statistically significance according to p-value estimation.  

## 4 
Let's have a look on boxplot showing heigh distribution between players from different countries -  
```{r}
soccer_wrk %>%
  with(
    boxplot(Height ~ Nationality, col = "cadetblue3", pch = 20,
            ylab = "Height (cm)")
  )
```
We can see that groups means almost identical. 

Now we can perform regression analysis.

```{r}
oneway.test(Height ~ Nationality, data = soccer_wrk)

```
As the result, we can not reject H0 - so there is no connection between heigh and nationality. 

Well, maybe HBW test can tell us more about it:
```{r}
m0 <- lm(Height ~ Nationality, data = soccer_wrk)
HBW.comp <- m0 %>%  glht(linfct = mcp(Nationality = "Tukey"))
HBW.comp %>% summary()
HBW.comp %>% confint()
HBW.comp %>% plot(xlab  = "Height difference (cm)")
```
Unfortunately, the results have confirmed and there is no significant dependence between heigh and nationality of players. 
